---
title: BFI screen sector statistics to September 2025
author: Brian Tarran
date: last-modified
date-format: long
format: 
  revealjs:
    smaller: true
css: style.css
title-slide-attributes:
  data-background-color: "#e50076"
execute: 
  echo: false
  warning: false
embed-resources: false
---

```{r}
#| label: load-functions
#| file: R/stats.R

```

```{r}
#| label: set-file-path

file_path <- here::here('data/bfi_stats_release_data.xlsx')
```

# UK box office and admissions {background-color="#e50076"}


##

<div id="left">

In the UK in the period January to September (Q1-3) 2025:

* Box office revenue was £751 million, up 10% on Q1-3 2024 and down 18% on Q1-3 2019.

</div>

<div id="right">

```{r}
#| label: uk-box-office
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

sheet_name <- "uk_box_office"
type <- "boxoffice"
data_and_vars <- load_data(file_path, sheet_name, type)
uk_box_office()
```

</div>

## 

<div id="left">

* There were 93 million cinema admissions, 4% higher than in Q1-3 2024 and 28% lower
than in Q1-3 2019.
* Figures are for all films on release, including event releases and those that started their release prior to the Q1-3 period.

</div>

<div id="right">

```{r}
#| label: uk-admissions
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

sheet_name <- 'uk_admissions'
data_and_vars <- load_data(file_path, sheet_name, type)
uk_admissions()
```
</div>

## 

<div id="left">

* July recorded 2025's highest monthly admissions to date, at 13 million.
* *Jurassic World Rebirth* and *Superman* were the highest earning releases of that month.

</div>

<div id="right">

```{r}
#| label: uk-admissions-month
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

uk_admissions_month()
```

</div>

# UK and Republic of Ireland box office {background-color="#783df6"}

##

<div id="left">

At the UK and Republic of Ireland (ROI) box office:

* Revenue for films released in Q1-3 2025 was £684.4 million, up 1% on Q1-3 2024 and
down 25% on Q1-3 2019.
* This excludes event releases.

</div>

<div id="right">

```{r}
#| label: uk-roi-box-office
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

sheet_name <- 'uk_roi_box_office'
data_and_vars <- load_data(file_path, sheet_name, type)
uk_roi_box_office()
```

</div>

```{r}
#| label: uk-market-share
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

sheet_name <- 'uk_film_share'
df <- load_data(file_path, sheet_name)
uk_market_share()
```

```{r}
#| label: uk-market-share-indie
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

uk_market_share_indie()
```

##

<div id="left">

* The total market share of all UK qualifying films was 43%, almost 12 percentage points higher than Q1-3 2024’s UK qualifying share.
* *Note*: 2025 figures in chart sum to 44% due to rounding.

</div>

<div id="right">

```{r}
#| label: uk-market-share-percent
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

sheet_name <- 'uk_film_share'
data_and_vars <- load_data(file_path, sheet_name, type)
uk_market_share_percent()
```

</div>

# Film and HETV production spend {background-color="#1197FF"}

```{r}
#| label: set-variables-spend

sheet_name <- 'uk_production_detail'
type <- 'production'
data_and_vars <- load_data(file_path, sheet_name, type)
metric <- 'UK_spend_m'
```

##

<div id="left">

In the UK, in the 12 months to September 2025: 

* The combined total spend on film and high-end television (HETV) production was £6.5 billion.
* This graph shows the figures that were 'first reported' for production spend in each 12-month period. 

</div>

<div id="right">

```{r}
#| label: all-production-first
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

all_production_first()
```

</div>

##

<div id="left">

* Production data is revised every period to account for lags in obtaining complete data across all types of productions.
* Combined spend for the 12 months to September 2025 was up 14% on revised figures for the previous 12-month period.

</div>

<div id="right">

```{r}
#| label: all-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

all_production_revised()
```

</div>

##

<div id="left">

* HETV accounted for 64% of UK production spend in the 12 months to September 2025.

</div>

<div id="right">

```{r}
#| label: film-hetv-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

film_hetv_production_revised()
```

</div>

```{r}
#| label: film-hetv-production-revised-percentage
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

film_hetv_production_revised_percentage()
```

##

<div id="left">

* UK spend on film production was £2.3 billion, up 6% compared with revised figures for the 12 months ending September 2024.

</div>

<div id="right">

```{r}
#| label: film-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
production_revised()
```

</div>

##

<div id="left">

The BFI assigns productions to one of three categories:

* Inward investment features (INW)
* Domestic UK features (DOM)
* Co-productions (COP)

See [notes to statistics releases](https://www.bfi.org.uk/industry-data-insights/official-statistics-release-calendar) for full definitions.

</div>

<div id="right">

```{r}
#| label: film-production-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
production_breakdown_revised()
```

</div>

##

<div id="left">

* UK spend on HETV projects was £4.2 billion in the 12 months to September 2025, up 19% on revised figures for the previous 12-month period.

</div>

<div id="right">

```{r}
#| label: hetv-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
production_revised()
```

</div>

##

<div id="left">

* Spend on all categories of production increased compared with revised figures for the 12 months to September 2024.
* *Note:* INW and COP spend is combined for the 12 months to September 2021 for reasons of disclosure control. 

</div>

<div id="right">

```{r}
#| label: hetv-production-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
production_breakdown_revised()
```

</div>

# Film and HETV production count {background-color="#1197FF"}

```{r}
#| label: set-variables-count

sheet_name <- 'uk_production_detail'
df <- load_data(file_path, sheet_name)
metric <- 'count'
```

##

<div id="left">

In the UK, in the 12 months to September 2025:

* Combined production starts were down 8% on first reported figures for the 12 months to September 2024.

</div>

<div id="right">

```{r}
#| label: all-production-count-first
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

all_production_first()
```

</div>

##

<div id="left">

* Production count for the 12 months to September 2025 is lower than for the other periods shown here. However, as previously noted, figures are likely to be revised upward in subsequent statistical releases as more data becomes available.

</div>

<div id="right">

```{r}
#| label: all-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

all_production_revised()
```

</div>

##

<div id="left">

* We saw earlier that HETV accounted for the majority of UK production spend in the 12 months to September 2025. In terms of number of productions, however, the split is almost even: 49% for film, 51% for HETV.

</div>

<div id="right">

```{r}
#| label: film-hetv-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

film_hetv_production_revised()
```

</div>

```{r}
#| label: film-hetv-production-count-revised-percentage
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

film_hetv_production_revised_percentage()
```

##

<div id="left">

* 167 films were recorded as starting principal photography in the UK in the 12 months to September 2025.

</div>

<div id="right">

```{r}
#| label: film-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
production_revised()
```

</div>

##

<div id="left">

* Lags in obtaining complete data on production activity tend to disproportionately affect counts for domestic UK feature films (DOM), particularly those with budgets of less than £500,000. 

</div>

<div id="right">

```{r}
#| label: film-production-count-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
production_breakdown_revised()
```

</div>

##

<div id="left">

* 171 HETV programmes were recorded as starting principal photography in the UK in the 12 months to September 2025.

</div>

<div id="right">

```{r}
#| label: hetv-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
production_revised()
```

</div>

##

<div id="left">

* HETV programme starts in the 12 months to September 2025 included 19 feature-length single episode productions.
* *Note:* INW and COP counts are combined for the 12 months to September 2021 for reasons of disclosure control.  

</div>

<div id="right">

```{r}
#| label: hetv-production-count-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
production_breakdown_revised()
```

</div>

# Certification {background-color="#e94e24"}

```{r}
#| label: load-cert

sheet_name <- 'certification'
type <- 'production'
data_and_vars <- load_data(file_path, sheet_name, type)
```

##

<div id="left">

In the 12 months to September 2025:

* A total of 585 films received final certification, either under the cultural test or as an official co-production.
* Certification is required to access UK tax reliefs and credits for audiovisual and video game expenditure.

</div>

<div id="right">

```{r}
#| label: film-cert-final-count
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
cert_status_select <- 'final'
metric <- 'count'
certification()
```

</div>

##

<div id="left">

* Films achieving final certification in the 12 months to September 2025 had an associated UK production spend of £1.9 billion.
* Films and other productions can apply for final certification when they have completed production and are ready to be released.

</div>

<div id="right">

```{r}
#| label: film-cert-final-spend
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
cert_status_select <- 'final'
metric <- 'uk_spend_m'
certification()
```

</div>

##

<div id="left">

* 281 HETV titles received final certification through the cultural test in the 12 months to September 2025.
* There were two co-productions with final certification but details are not included for disclosure control reasons.

</div>

<div id="right">

```{r}
#| label: hetv-cert-final-count
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
cert_status_select <- 'final'
metric <- 'count'
certification()
```

</div>

##

<div id="left">

* HETV productions receiving final certification under the cultural test in the 12 months to September 2025 had a UK production spend of £4.7 billion.

</div>

<div id="right">

```{r}
#| label: hetv-cert-final-spend
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
cert_status_select <- 'final'
metric <- 'uk_spend_m'
certification()
```

</div>

##

<div id="left">

* 72 animation television programmes received final certification under the cultural test in the 12 months to September 2025.
* There were two co-productions with final certification but details are not included for disclosure control reasons.

</div>

<div id="right">

```{r}
#| label: animation-cert-final-count
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'animation_tv'
cert_status_select <- 'final'
metric <- 'count'
certification()
```

</div>

##

<div id="left">

* Animation TV productions receiving final certification under the cultural test in the 12 months to September 2025 had a UK production spend of £196 million.

</div>

<div id="right">

```{r}
#| label: animation-cert-final-spend
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'animation_tv'
cert_status_select <- 'final'
metric <- 'uk_spend_m'
certification()
```

</div>

##

<div id="left">

* 101 children’s television programmes received final certification under the cultural test in the 12 months to September 2025.
* There were two co-productions with final certification but details are not included for disclosure control reasons.

</div>

<div id="right">

```{r}
#| label: childrens-cert-final-count
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'childrens_tv'
cert_status_select <- 'final'
metric <- 'count'
certification()
```

</div>

##

<div id="left">

* Children's TV productions receiving final certification under the cultural test in the 12 months to September 2025 had a UK production spend of £134 million.

</div>

<div id="right">

```{r}
#| label: childrens-cert-final-spend
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'childrens_tv'
cert_status_select <- 'final'
metric <- 'uk_spend_m'
certification()
```

</div>

##

<div id="left">

* 256 video games received final certification in the 12 months to September 2025.
* Video games can only be certified under the cultural test.

</div>

<div id="right">

```{r}
#| label: video-games-cert-final-count
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'video_games'
cert_status_select <- 'final'
metric <- 'count'
certification()
```

</div>

##

<div id="left">

* Video games receiving final certification in the 12 months to September 2025 had a UK production spend of £736 million.
* This is the second highest UK spend figure on record.

</div>

<div id="right">

```{r}
#| label: video-games-cert-final-spend
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'video_games'
cert_status_select <- 'final'
metric <- 'uk_spend_m'
certification()
```

</div>

# Sources {background-color="#e50076"}

* Box office: Comscore, BFI Research & Statistics Unit
* Admissions: Cinema Advertising Association
* Production: BFI Research & Statistics Unit
* Certification: BFI Research & Statistics Unit, BFI Certification Unit 

See [bfi.org.uk](https://www.bfi.org.uk/industry-data-insights) for more industry data and insights